\mytitile\\~

### 2019-11-09 document.tex
Transition probabilities
Added experimental zoom

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{stationary}
	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid. The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:statinary_levels}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{zoom_picture}
	\caption{Zoomed-in simulation of feature III with increasing amplitude of the driving of the first transmon $\Omega_1/2\pi=$2, 4, 10 and 20 MHz while the second drive is fixed at $\Omega_2/2\pi=$10 MHz; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state ($\ket{00}$). The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect. Interestingly, population inversion is observed inside the red-coloured areas of the graph: $\ket{00}$ population is less than 20\% there.}
	\label{fig:zoom}
\end{figure}

>>>>

\begin{figure*}
	\includegraphics[width=.49\linewidth]{powerscan}
	\includegraphics[width=.49\linewidth]{zoom2_picture}
	\caption{Investigation of the power dependence of feature II. \textbf{(a)} Experiment (second cooldown, the parameters are different). The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed. \textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4, 8, 15 and 30; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state ($\ket{00}$). The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
	\label{fig:zoom}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{stationary}
	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid. The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:statinary_levels}
\end{figure*}

@@
